---
title: "Reproducible Research: Peer Assessment 1"
author: "Sam Edgemon"
date: "April 16, 2015"
output: 
  html_document:
    keep_md: true
---
#### Test3

#### Loading and Processing the Data

- set my working directory
- read in the zipped file, unzip it, and save it as "data"
- format date

```{r getdata}
setwd("~/GitHub/RepData_PeerAssessment1")  
activity <- read.table(unz("activity.zip", "activity.csv"), header=T, quote="\"", sep=",")   
activity$date <- as.Date(activity$date)
```
  
### What is mean total number of steps taken per day?

- Built dataset without missings
- Found daily steps
- Produced Mean
- Produced Median
- Produced Histogram

```{r}
activity.ignore.na <- na.omit(activity)
daily.steps <- rowsum(activity.ignore.na$steps, format(activity.ignore.na$date, '%Y-%m-%d')) 
daily.steps <- data.frame(daily.steps) 
names(daily.steps) <- ("steps") 

mean(daily.steps$steps)
median(daily.steps$steps)

hist(daily.steps$steps, 
     main=" ",
     breaks=10,
     ylim=c(0, 30),
     xlab="Total Number of Steps Taken Daily")
```


### What is the average daily activity pattern?

- load libraries
- create a variable called interval.mean.steps
- qplot
- identify interval with max steps

```{r}
library(plyr)
library(ggplot2)
interval.mean.steps <- ddply(activity.ignore.na,~interval, summarise, mean=mean(steps))
qplot(x=interval, y=mean, data = interval.mean.steps,  geom = "line",
      xlab="5-Minute Interval",
      ylab="Step Count",
      main="Average Steps Taken - Averaged Across All Days"
      )

# Maximum steps occurs on this interval:
interval.mean.steps[which.max(interval.mean.steps$mean), ]
```



### Imputing missing values

```{r}
# Number of Records with missing values
activity_NA <- sum(is.na(activity))

# Create a copy of the original data set - activity_i "activity impute"
activity_i <- activity

# Replace all NA steps values with the average number of steps for that interval
which <- which(is.na(activity$steps))
intervals <- activity[which, "interval"]
activity_i[which, "steps"] <- interval.mean.steps[interval.mean.steps == activity[which, "interval"], "mean"]

daily.steps <- rowsum(activity_i$steps, format(activity_i$date, '%Y-%m-%d')) 
daily.steps <- data.frame(daily.steps) 
names(daily.steps) <- ("steps") 

hist(daily.steps$steps, 
     main=" ",
     breaks=10,
     ylim=c(0, 30),
     xlab="Total Number of Steps Taken Daily (after imputation of missing values)")
```


### Are there differences in activity patterns between weekdays and weekends?

- build logical data frame of days
- create a new variable called weekday
-- assign logical values to weekday and weekend designations
- repeat an earlier step and get averages per interval
- create sub-plots by type 

```{r}
days <- weekdays(as.Date(activity$date)) %in% c('Saturday','Sunday')
activity$weekday <- factor(days, labels = c("weekday", "weekend"))
steps_per_interval_weekday_avg <- aggregate(steps ~ interval + weekday, activity, FUN = mean)

g <- ggplot(steps_per_interval_weekday_avg, aes(x = interval, y = steps))
g <- g + facet_wrap(~ weekday, ncol = 1)
g <- g + geom_line()
g <- g + labs(x = "Interval")
g <- g + labs(y = "Mean Number of Steps")
g
```

### END Peer Assessment 1